SAYCAM preprocessing analyses from bounding box outputs

### 2021-12-21 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd

## Paths to raw outputs & datafiles
```{r}
# toggle between each of these folders / dataset types
# dataset_dir = "/data/bounding_boxes/"; dataset_type = "all_detections"
dataset_dir = "/data/high_conf_bounding_boxes/"; dataset_type = "high_conf_detections"

@@

all_vid_data <- all_vid_data %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
```

@@

>>>>

## Paths to raw outputs & datafiles
```{r}
# toggle between each of these folders / dataset types
dataset_dir = "/data/bounding_boxes/"; dataset_type = "all_detections"
# dataset_dir = "/data/high_conf_bounding_boxes/"; dataset_type = "high_conf_detections"

@@

all_vid_data <- all_vid_data %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))

@@

### Get gold sample detections by sweeping across detection thresholds
```{r}
reload_data=TRUE
# redo gold sample 
if (reload_data){
vid_index = 0
## load gold sample annotations

all_thresholds = seq(0,.9,.1)

   # now get vid level data

   for (detection_thres in all_thresholds){

      gold_sample_op_this_thres <- this_vid_data %>%
        filter(frame %in% frames_to_get$frame) %>%
        mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
        group_by(frame, vid_name, child_id) %>%
        summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>detection_thres) %>%
        mutate(detection_threshold = detection_thres)

      if (detection_thres==0){
         gold_sample_op<-gold_sample_op_this_thres
      }
      else if (detection_thres>0){
      gold_sample_op <- gold_sample_op %>%
        full_join(gold_sample_op_this_thres)
      }
   }

## Add in age data
all_gold_sample_frames_op <-all_gold_sample_frames_op %>%
  mutate(date_filmed = lubridate::ymd(str_split_fixed(vid_name,"_",4)[[2]])) %>%
  left_join(age_info) %>%
  rowwise() %>%
  mutate(age_days = as.numeric(difftime(date_filmed,bday)))

save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_from_bbs_2021_',dataset_type,'all_thresholds.RData')))
